Databrary: Enabling Sharing and Reuse of Research Video

### 2015-06-18 jcdl-15/poster/poster_landscape.tex
fix typo
alphabetical order for names
a word
Fix postresql typo in jcdl poster

%%
\begin{poster}%
  % Poster Options
  {
  % Show grid to help with alignment
  grid=false,
  % Column spacing
  colspacing=1em,
  columns=3,
  % Color style
  bgColorOne=white,
  bgColorTwo=white,
  borderColor=dbrary,
  headerColorOne=dbrary,
  headerColorTwo=dbrary,
  headerFontColor=white,
  boxColorOne=white,
  boxColorTwo=dbrary,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=true,
  headerborder=closed,
  headerheight=0.1\textheight,
%  textfont=\sc, An example of changing the text font
  headershape=roundedright,
  headershade=shadelr,
  headerfont=\Large\bf\textsc, %Sans Serif
  textfont={\setlength{\parindent}{1.5em}},
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  {
    \includegraphics[height=5em]{img/datavyu-leaf-large.png}
  } 
  %Title
  {\bf{Databrary: Enabling Sharing and Reuse of Research Video} }
  % Authors
  { Andrew S. Gordon \emph{(drew@databrary.org)}, Rick O. Gilmore, Karen E. Adolph, David S. Millman, Lisa Steiger, and Dylan A. Simon \\
  JCDL 2015}
  % University logo
  {
    \includegraphics[height=5em]{img/databrary-leaf-large.png}
  }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Access Restrictions}{name=access,column=0,row=1, below=abstract}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      Databrary ensures that identifiable information in videos can shared under four different release levels:
        \begin{center}
        \includegraphics[width=\textwidth]{img/release_levels.png}
        \end{center}
  }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Technology Stack}{name=stack,column=2,span=1,row=0,bottomaligned=splash}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    Databrary is built on PostreSQL using the Scala Play framework and AngularJS.
    Data are preserved indefinitely in a secure data storage facility at NYU. 
    There is no cost to use the system; a sustainability model is under development.
    All code is GPL on GitHub.
    \begin{center}
    \includegraphics[width=.9\textwidth]{img/architecture.png}
    \end{center}
  }

>>>>

%%
\begin{poster}%
  % Poster Options
  {
  % Show grid to help with alignment
  grid=false,
  % Column spacing
  colspacing=1em,
  columns=3,
  % Color style
  bgColorOne=white,
  bgColorTwo=white,
  borderColor=dbrary,
  headerColorOne=dbrary,
  headerColorTwo=dbrary,
  headerFontColor=white,
  boxColorOne=white,
  boxColorTwo=dbrary,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=true,
  headerborder=closed,
  headerheight=0.1\textheight,
%  textfont=\sc, An example of changing the text font
  headershape=roundedright,
  headershade=shadelr,
  headerfont=\Large\bf\textsc, %Sans Serif
  textfont={\setlength{\parindent}{1.5em}},
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  {
    \includegraphics[height=5em]{img/datavyu-leaf-large.png}
  } 
  %Title
  {\bf{Databrary: Enabling Sharing and Reuse of Research Video} }
  % Authors
  { Andrew S. Gordon \emph{(drew@databrary.org)}, Karen E. Adolph, Rick O. Gilmore, David S. Millman, Lisa Steiger, and Dylan A. Simon \\
  JCDL 2015}
  % University logo
  {
    \includegraphics[height=5em]{img/databrary-leaf-large.png}
  }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Access Restrictions}{name=access,column=0,row=1, below=abstract}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      Databrary ensures that data with identifiable information can be shared under four different release levels:
        \begin{center}
        \includegraphics[width=\textwidth]{img/release_levels.png}
        \end{center}
  }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Technology Stack}{name=stack,column=2,span=1,row=0,bottomaligned=splash}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    Databrary is built on PostgreSQL using the Scala Play framework and AngularJS.
    Data are preserved indefinitely in a secure data storage facility at NYU. 
    There is no cost to use the system; a sustainability model is under development.
    All code is GPL on GitHub.
    \begin{center}
    \includegraphics[width=.9\textwidth]{img/architecture.png}
    \end{center}
  }
